Surrogate Regret Bounds for Polyhedral Losses

### 2021-10-22 rates-neurips-21/rates.tex
rates camera - first pass

%\usepackage[preprint]{neurips_2021}  % for arxiv
%\usepackage[final]{neurips_2021}     % camera ready
\usepackage[nonatbib]{neurips_2021}             % USE THIS for paper submission

@@

@@

\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
\usepackage{bbm}
\usepackage{amsmath,amsthm,amsfonts,amssymb}

@@

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
% \DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Surrogate Regret Bounds for Polyhedral Losses}
%Rate Transfers with Polyhedral Surrogate Losses
% \And separates authors; \AND separates with forced line break
\author{%
  Rafael Frongillo \\
  U. Colorado, Boulder \\
  \texttt{raf@colorado.edu} \\
  \And
  Bo Waggoner \\
  U. Colorado, Boulder \\
  \texttt{bwag@colorado.edu}
}

@@

\begin{abstract}
  Surrogate risk minimization is an ubiquitous paradigm in supervised machine learning, wherein a target problem is solved by minimizing a surrogate loss on a dataset.
  Surrogate regret bounds, also called excess risk bounds, are a common tool to prove generalization rates for surrogate risk minimization.
  While surrogate regret bounds have been developed for certain classes of loss functions, such as proper losses, general results are relatively sparse.
  We provide two general results.
  The first gives a linear surrogate regret bound for any polyhedral (piecewise-linear convex) surrogate, meaning that surrogate generalization rates translate directly to target rates.
  The second shows that for sufficiently non-polyhedral surrogates, the regret bound is a square root, meaning fast surrogate generalization rates translate to slow rates for the target.
  Together, these results suggest polyhedral surrogates are weakly optimal in many cases.
  \raf{Todos:
    * cite IEEE paper (doh...)
    * cite Zalinescu~\cite{zalinescu2003sharp} for Hoffman constants}
\end{abstract}

@@

%As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear near $0$, the overall rate would have been a fast $O(1/n)$.
\raft{Maybe a good place to cite the IEEE rates paper}
Much is known about surrogate regret bounds for particular problems, especially for binary classification and related problems like bipartite ranking; see \S~\ref{sec:related-work} for a discussion of the literature.
General results which span multiple target problems, however, are sparse.
%, often forcing authors to prove bounds for specific surrogate losses from scratch, e.g.~\cite{ramaswamy2015hierarchical,ramaswamy2018consistent}.
Furthermore, we still lack guidance as to which surrogate will lead to the best overall target generalization rate, as this rate depends on both the surrogate generalization rate and the regret transfer function.
For example, consider the choice between a \emph{polyhedral} (piecewise-linear and convex) surrogate, like hinge loss, or a smooth surrogate like exponential or squared loss.
The surrogate rate for polyhedral losses will likely be a slower $O(1/\sqrt{n})$, whereas one typically achieves a faster $O(1/n)$ rate with smooth surrogates---but what is the tradeoff when it comes to the regret transfer function $\zeta$, which ultimately decides the target generalization rate?
To answer these types of questions, we need more general results.

Our first result is a general surrogate regret bound for polyhedral surrogates.
% Examples include hinge loss, the abstain loss of \bo{cite ramaswamy}, \bo{and others?}
Perhaps suprisingly, we show that \emph{every} consistent surrogate in this class achieves a linear regret transfer, meaning their surrogate generalization rates translate directly to target rates, up to a constant factor.
  % \begin{theorem}[Linear bounds for polyhedral surrogates]
\begin{theorem}[Linear bound for polyhedral]
  \label{thm:main-upper}
  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
  Then $L$ satisfies Equation \ref{eq:surrogate-regret-bound-informal} with a linear $\zeta$.
  %Then there is a linear regret transfer function $\zeta$.
  % Then $(L,\psi)$ guarantee a linear regret transfer function $\zeta$ to $\ell$.
\end{theorem}
The recent embedding framework of~\citet{finocchiaro2019embedding} shows how to construct consistent polyhedral surrogates for any discrete target loss; Theorem~\ref{thm:main-upper} additionally endows these surrogates with linear regret bounds.
In particular, this result immediately applies to the Weston--Watkins surrogate~\cite{wang2020weston}, Lov\'asz hinge~\cite{yu2018lovasz,finocchiaro2019embedding}, and other polyhedral surrogates in the literature currently lacking regret bounds.

We also give a partial converse: If the surrogate is sufficiently ``non-polyhedral'', i.e. smooth and locally strongly convex, then $\zeta$ cannot shrink faster than a square root.
For these losses, therefore, even fast surrogate generalization rates would likely translate to slow rates for the target.
%This result could be viewed as a partial converse to the first, providing evidence that some element of piecewise-linearity is necessary for optimal surrogate regret bounds.
\begin{theorem}[Lower bound for ``non-polyhedral'']
  \label{thm:main-lower}
  Let $L$ be a locally strongly convex surrogate with locally Lipschitz gradient.
  If $L$ satisfies Equation \ref{eq:surrogate-regret-bound-informal} for a target loss $\ell$, then there exists $c>0$ such that, for all small enough $\epsilon \geq 0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
\end{theorem}
% Thus, polyhedral losses are not only order-optimal in terms of regret transfer, but a significant element of piecewise-linearity seems \emph{necesseary} for optimal transfer.
While it may seem intuitive that $\zeta=\sqrt{\cdot}$ for strongly convex losses, it is well-known that losses like exponential loss for binary classification also have $\zeta=\sqrt{\cdot}$, even though they are neither strongly convex nor strongly smooth~\cite{bartlett2006convexity}.
Theorem~\ref{thm:main-lower} offers an explanation for this phenomenon, and together with Theorem~\ref{thm:main-upper} clarifies an intriguing trend in the literature: $\zeta$ is typically either linear or square-root.

Taken together, our results shed light on the dichotomy expressed above: slower polyhedral surrogate rates of $O(1/\sqrt{n})$ will translate to the target unchanged, while most smooth surrogates, even if achieving a fast surrogate generalization rate of $O(1/n)$, will likely yield the same target rate of $O(1/\sqrt{n})$.
Our results therefore suggest an inherent tradeoff fast surrogate rates and optimal regret transfer, a phenomenon also observed by~\citet{mahdavi2014binary} for binary classification.
In particular, our results suggest that polyhedral losses may be weakly optimal in many cases.
% This result may be at odds with the smoothness and strong convexity properties often used to show fast convergence rates for convex surrogates \bo{cite?}.
% We leave to other work the possibility of an inherent tradeoff between fast surrogate convergence and optimal regret transfer; this question is explored to an extent in \bo{IEEE paper}.

Our proof of the upper bound, Theorem \ref{thm:main-upper}, is nonconstructive.
After proving the main results (Sections \ref{sec:upper} and \ref{sec:lower}), we make it constructive in Section \ref{sec:constant}.
Specifically, a polyhedral loss's regret transfer function can be bounded by $\zeta(t) \leq \alpha \cdot t$ where the constant is of the form $\alpha = \alpha_{\ell} \cdot \alpha_L \cdot \alpha_{\psi}$.
Each component of $\alpha$ is constructed as a function of its respective object $\ell$, $L$, and $\psi$.
A corollary of the derivation is that a polyhedral loss $L$ and link $\psi$ are consistent for $\ell$ if and only if they satisfy the weak indirect elicitation criterion and $\psi$ is \emph{$\epsilon$-separated}, a condition introduced in \citet{finocchiaro2019embedding}.

@@

@@

Perhaps closest in spirit to our work are several recent works on general structured prediction problems.
\citet[Theorem 2]{ciliberto2016consistent} and \citet[Theorem 7]{osokin2017structured} give surrogate regret bounds for a quadratic surrogate, for a general class of structed prediction problems.
\citet[Proposition 5]{blondel2019structured} gives surrogate regret bounds for a tighter class of quadratic surrogates based on projection oracles.
\citet[Theorem 4.4]{nowak2019general} give even more general bounds, using a broader class of surrogates based on estimating a vector-valued expectation.
All of these works apply to a broad range of discrete target problems.
The main difference to our work is that their upper bounds are all for strongly convex surrogates,%
\footnote{These works express surrogate regret bounds with $\zeta^{-1}$ appearing on the left-hand side of eq.~\eqref{eq:surrogate-regret-bound-informal}, and thus the terms ``upper bound'' and ``lower bound'' are reversed from their terminology.}
whereas ours are for polyhedral surrogates.
\citet[Theeorem 8]{osokin2017structured} and \citet[Theorem 4.5]{nowak2019general} also provide lower bounds, in the same spirit as our Theorem~\ref{thm:main-lower} but only for the classes of surrogates they study.
In particular, our results recover their bounds up to a constant factor.

@@

\paragraph{Target problems.}
We consider supervised machine learning problems where data points have features in $\X$ and labels in $\Y$, a finite set.
The \emph{target problem} is to learn a hypothesis mapping $\X$ to a \emph{report} (or \emph{prediction}) \emph{space} $\R$, possibly different from $\Y$.
For example, binary classification has $\Y = \R = \{-1,+1\}$, whereas for ranking problems $\R$ may be the set of permutations of $\Y$.
%, or $\R=\Y\cup\{\bot\}$ for classification with an abstain option.
In this paper, we assume $\R$ is a finite set.
%For example, standard binary classification has $\Y = \R = \{-1,+1\}$, whereas in a ranking problem, $\R$ is the set of all permutations of $\Y$.
The target problem is specified by the \emph{target loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r \in \R$ to the vector $\ell(r)$ of nonnegative loss values for each label, i.e. $\ell(r) = (\ell(r)_y)_{y\in\Y}$.
Given a hypothesis $g: \X \to \R$ and a data point $(x,y) \in \X \times \Y$, the loss is $\ell(g(x))_y$.
We make a minimal non-redundancy assumption on $\ell$, formalized in Section \ref{subsec:elic}.
We may refer to $\ell$ as a \emph{discrete} target loss to emphasize our assumption that $\R$ and $\Y$ are finite.

\paragraph{Surrogate problems.}
We recall the surrogate risk minimization framework.
First, one constructs a \emph{surrogate loss function} $L:\reals^d\to\reals^\Y_+$.
Then, one minimizes it to learn a hypothesis of the form $h: \X \to \reals^d$.
Finally, one applies a \emph{link function} $\psi: \reals^d \to \R$, which maps $h$ to the implied target hypothesis $\psi \circ h$.
In other words, if a surrogate prediction $h(x) \in \reals^d$ implies a prediction $\psi(h(x)) \in \R$ for the target problem.
For example, in binary classification, the target problem is given by $0$-$1$ loss, $\ell(r)_y = \ones\{r\neq y\}$, with surrogate losses typically defined over $\reals$.
Common surrogate losses include hinge loss and logistic loss.
These surrogates are typically associated with the link $\psi(u) = \mathrm{sign}(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$.

@@

\section{Upper Bound: Polyhedral Surrogates} \label{sec:upper}
In this section, we describe the proof of Theorem \ref{thm:main-upper}, that polyhedral surrogates guarantee linear regret transfers.
At a high level, the proof (whose details appear in Appendix \ref{app:upper}) has two parts:
\begin{enumerate}
\item Fix $p\in\simplex$.
  Prove a regret bound for this fixed $p$, namely a constant $\alpha_p$ such that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for all $u\in\reals^d$.
      \item Apply this regret bound to each $p$ in a carefully chosen finite subset of $\simplex$.
        Argue that the maximum $\alpha_p$ from this finite set suffices for the overal regret bound.
\end{enumerate}
The first part will actually hold for any calibrated surrogate.
The second part relies on a crucial fact about polyhedral losses $L$: their properties $\Gamma=\prop{L}$ cover the whole simplex with only a finite number of polyhedral level sets~\cite{finocchiaro2019embedding}.
Thus, although the prediction space $\reals^d$ is infinite, one can restrict to just a finite set of prediction points and always have a global minimizer of expected surrogate loss.

\subsection{Linear transfer for fixed $p$}
First, we establish a linear transfer for any fixed conditional distribution $p$.
This holds for any calibrated surrogate, not necessarily polyhedral.
\begin{lemma} \label{lemma:fixed-p}
  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss and suppose the surrogate $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are calibrated for $\ell$.
  Then for any $p \in \simplex$, there exists $\alpha_p \geq 0$ such that, for all $u \in \reals^d$,
    \[ R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p) . \]
\end{lemma}
While this result is nice, it is also somewhat nonconstructive and potentially loose.
In Section \ref{sec:constant}, we investigate the constant $\alpha_p$ for polyhedral losses in particular.

\subsection{Linear overall transfer function}
Given Lemma \ref{lemma:fixed-p}, we might hope to obtain that, for any calibrated surrogate, there exists $\alpha = \sup_p \alpha_p$ such that $R_{\ell}(\psi(u),p') \leq \alpha R_L(u,p')$ for all $p'$.
However, we know this is false in general: not all surrogates yield linear regret transfers!
Indeed, for many surrogates, the supremum will be $+\infty$.

@@

The next lemma states that surrogate regret is linear in $p$ on any fixed level set $\Gamma_{u^*}$ of $\Gamma = \prop{L}$.
By combining this fact with Lemma \ref{lemma:refines}, we obtain that target regret is linear on these level sets as well.
\begin{lemma} \label{lemma:linear-on-levelset}
  Suppose $(L,\psi)$ indirectly elicits $\gamma = \prop{\ell}$ and let $\Gamma = \prop{L}$.
  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $R_L(u,\cdot)$ and $R_{\ell}(r,\cdot)$ are linear on $\Gamma_{u^*}$ in their second arguments.
\end{lemma}

We now arrive at the key fact about polyhedral losses we will use.
% It requires that $L$ be \emph{minimizable:} for all $p \in \simplex$, there exists some optimal prediction $u$, i.e. where $\inprod{p}{L(u)} = \inf_{u' \in \reals^d} \inprod{p}{L(u')}$.
% Note that if $(L,\psi)$ indirectly elicits $\ell$ for some $\psi$ and $\ell$ then $L$ is minimizable.
% \raf{Fix discussion and proof: minimizability comes for free, since we assume $L(\cdot)_y \geq 0$ for all $y$.}
\begin{lemma} \label{lemma:polyhedral-finite}
  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$.
  Moreover, these level sets are polytopes.
\end{lemma}

>>>>

%\usepackage[preprint]{neurips_2021}  % for arxiv
\usepackage[final,nonatbib]{neurips_2021}     % camera ready
%\usepackage[nonatbib]{neurips_2021}             % USE THIS for paper submission

@@

% apparently monospaced fonts cause type 3 font problems and this fixes it... https://tex.stackexchange.com/questions/73766/location-of-type3-font-being-used-in-my-document
\renewcommand{\ttdefault}{lmtt}

@@

\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
% \usepackage{bbm}
\usepackage{dsfont}   % mathbbm is type 3 = bad (bitmapped) font
\usepackage{amsmath,amsthm,amsfonts,amssymb}

@@

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathds{1}}  % mathbbm is type 3 = bad (bitmapped) font
% \newcommand{\ones}{\mathbbm{1}}
\newcommand{\indopp}{\bar{\ones}}
% \DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Surrogate Regret Bounds for Polyhedral Losses}
%Rate Transfers with Polyhedral Surrogate Losses
% \And separates authors; \AND separates with forced line break
\author{%
  Rafael Frongillo \\
  University of Colorado Boulder \\
  \texttt{raf@colorado.edu} \\
  \And
  Bo Waggoner \\
  University of Colorado Boulder \\
  \texttt{bwag@colorado.edu}
}

@@

\begin{abstract}
  Surrogate risk minimization is an ubiquitous paradigm in supervised machine learning, wherein a target problem is solved by minimizing a surrogate loss on a dataset.
  Surrogate regret bounds, also called excess risk bounds, are a common tool to prove generalization rates for surrogate risk minimization.
  While surrogate regret bounds have been developed for certain classes of loss functions, such as proper losses, general results are relatively sparse.
  We provide two general results.
  The first gives a linear surrogate regret bound for any polyhedral (piecewise-linear and convex) surrogate, meaning that surrogate generalization rates translate directly to target rates.
  The second shows that for sufficiently non-polyhedral surrogates, the regret bound is a square root, meaning fast surrogate generalization rates translate to slow rates for the target.
  Together, these results suggest polyhedral surrogates are optimal in many cases.

  \bigskip

\begin{verbatim}
TODOS:
examples (google doc)
X clarify regret bounds for inconsistent losses (google doc)
add references (below)

update abstract in openreview
add keywords in openreview
ask bo for feedback
double check camera-ready email
\end{verbatim}

\end{abstract}

@@

%As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear near $0$, the overall rate would have been a fast $O(1/n)$.
Much is known about surrogate regret bounds for particular problems, especially for binary classification and related problems like bipartite ranking; see \S~\ref{sec:related-work} for a discussion of the literature.
General results which span multiple target problems, however, are sparse.
%, often forcing authors to prove bounds for specific surrogate losses from scratch, e.g.~\cite{ramaswamy2015hierarchical,ramaswamy2018consistent}.
Furthermore, we still lack guidance as to which surrogate will lead to the best overall target generalization rate, as this rate depends on both the surrogate generalization rate and the regret transfer function.
For example, consider the choice between a \emph{polyhedral} (piecewise-linear and convex) surrogate, like hinge loss, or a smooth surrogate like exponential or squared loss.
The surrogate rate for polyhedral losses will likely be a slower $O(1/\sqrt{n})$, whereas one typically achieves a faster $O(1/n)$ rate with smooth surrogates---but what is the tradeoff when it comes to the regret transfer function $\zeta$, which ultimately decides the target generalization rate?
To answer these types of questions, we need more general results.

Our first result is a general surrogate regret bound for polyhedral surrogates.
% Examples include hinge loss, the abstain loss of \bo{cite ramaswamy}, \bo{and others?}
Perhaps surprisingly, we show that \emph{every} consistent surrogate in this class achieves a linear regret transfer, meaning their surrogate generalization rates translate directly to target rates, up to a constant factor.
  % \begin{theorem}[Linear bounds for polyhedral surrogates]
\begin{theorem}[Linear bound for polyhedral]
  \label{thm:main-upper}
  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
  Then $L$ satisfies Equation~\ref{eq:surrogate-regret-bound-informal} with a linear $\zeta$.
  %Then there is a linear regret transfer function $\zeta$.
  % Then $(L,\psi)$ guarantee a linear regret transfer function $\zeta$ to $\ell$.
\end{theorem}
The recent embedding framework of~\citet{finocchiaro2019embedding} shows how to construct consistent polyhedral surrogates for any discrete target loss; Theorem~\ref{thm:main-upper} additionally endows these surrogates with linear regret bounds.
In particular, this result immediately applies to the Weston--Watkins surrogate~\cite{wang2020weston}, Lov\'asz hinge~\cite{yu2018lovasz,finocchiaro2019embedding}, and other polyhedral surrogates in the literature currently lacking regret bounds.%
\footnote{\raf{Bo: check me.  Clear/detailed enough?  Right place / okay to footnote?  We promised two reviewers a clarification of this point.}
  Many of these polyhedral surrogates are actually known to be \emph{inconsistent} for their intended target problems.
  Nonetheless, the embedding framework of \citet{finocchiaro2019embedding} shows that any polyhedral surrogate is consistent for \emph{some} target problem, namely the one that it embeds.
  It is to this embedded target loss function that our linear regret bounds apply.
Moreover, the same authors show that any discrete target loss has a consistent polyhedral surrogate, to which our bounds apply as well.}

We also give a partial converse: If the surrogate is sufficiently ``non-polyhedral'', i.e. smooth and locally strongly convex, then $\zeta$ cannot shrink faster than a square root.
For these losses, therefore, even fast surrogate generalization rates would likely translate to slow rates for the target.
%This result could be viewed as a partial converse to the first, providing evidence that some element of piecewise-linearity is necessary for optimal surrogate regret bounds.
\begin{theorem}[Lower bound for ``non-polyhedral'']
  \label{thm:main-lower}
  Let $L$ be a locally strongly convex surrogate with locally Lipschitz gradient.
  If $L$ satisfies Equation~\ref{eq:surrogate-regret-bound-informal} for a target loss $\ell$, then there exists $c>0$ such that, for all small enough $\epsilon \geq 0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
\end{theorem}
% Thus, polyhedral losses are not only order-optimal in terms of regret transfer, but a significant element of piecewise-linearity seems \emph{necesseary} for optimal transfer.
While it may seem intuitive that $\zeta=\sqrt{\cdot}$ for strongly convex losses, it is well-known that losses like exponential loss for binary classification also have $\zeta=\sqrt{\cdot}$, even though they are neither strongly convex nor strongly smooth~\cite{bartlett2006convexity}.
Theorem~\ref{thm:main-lower} offers an explanation for this phenomenon, and together with Theorem~\ref{thm:main-upper} clarifies an intriguing trend in the literature: $\zeta$ is typically either linear or square-root.

Taken together, our results shed light on the dichotomy expressed above: slower polyhedral surrogate rates of $O(1/\sqrt{n})$ will translate to the target unchanged, while most smooth surrogates, even if achieving a fast surrogate generalization rate of $O(1/n)$, will likely yield the same target rate of $O(1/\sqrt{n})$.
Our results therefore suggest an inherent tradeoff fast surrogate rates and optimal regret transfer, a phenomenon also observed by~\citet{mahdavi2014binary} for binary classification.
In particular, our results suggest that polyhedral losses may achieve an overall generalization rate to the target problem with the optimal dependence on the number of data points.
% This result may be at odds with the smoothness and strong convexity properties often used to show fast convergence rates for convex surrogates \bo{cite?}.
% We leave to other work the possibility of an inherent tradeoff between fast surrogate convergence and optimal regret transfer; this question is explored to an extent in \bo{IEEE paper}.

The proof of our upper bound, Theorem~\ref{thm:main-upper}, is nonconstructive.
After proving the main results (Sections~\ref{sec:upper} and~\ref{sec:lower}), we make it constructive in Section~\ref{sec:constant}.
Specifically, the regret transfer function for a polyhedral loss can be bounded by $\zeta(t) \leq \alpha \cdot t$ where the constant is of the form $\alpha = \alpha_{\ell} \cdot \alpha_L \cdot \alpha_{\psi}$.
Each component of $\alpha$ depends only on its respective object $\ell$, $L$, and $\psi$.
A corollary of the derivation is that a polyhedral loss $L$ and link $\psi$ are consistent for $\ell$ if and only if they satisfy the weak indirect elicitation criterion and $\psi$ is \emph{$\epsilon$-separated}, a condition introduced in \citet{finocchiaro2019embedding}.

@@

\hrule

  \raf{cite IEEE paper (doh...)}

  \bigskip

More references related to calibration/excess risk bound for other specific problems that the authors may want to include in the manuscript.

Binary classification with rejection:

[1] Cortes et al., Learning with rejection, ALT, 2016 (Theorem 3 - a variant of hinge loss with linear excess risk bound). FYI: There exists another work by the same authors where they used an exponential-based loss for this problem with calibration guarantee [2], but unfortunately the excess risk bound was not provided to my knowledge (but I guess it would be slower than linear).

[2] Cortes et al., Boosting with abstention, NeurIPS, 2016

Multiclass classification with rejection:

[3] Ni et al., On the calibration of multiclass classification with rejection, NeurIPS, 2019 (Theorem 7 (Bound for OVA loss based on strictly proper composite loss choice (square root rate for many losses according to Table 1)) and Theorem 8 (Bound for softmax cross-entropy loss (square root rate)).

[4] Charoenphakdee et al., Classification with rejection based on cost-sensitive classification, ICML, 2021 (Theorem 8 (excess risk transfer bound for classification with rejection and general classification-calibrated loss) and Corollary 9 (Excess risk bound of hinge loss with linear rate)).

Bipartite ranking:

[5] Gao and Zhou, On the consistency of AUC pairwise optimization, IJCAI, 2015 (Theorem 3 and Corollary 5, where Corollary 5 indicates that exponential and logistic losses give a square root regret bound).

\hrule

@@

Perhaps closest in spirit to our work are several recent works on general structured prediction problems.
\citet[Theorem 2]{ciliberto2016consistent} and \citet[Theorem 7]{osokin2017structured} give surrogate regret bounds for a quadratic surrogate, for a general class of structed prediction problems.
\citet[Proposition 5]{blondel2019structured} gives surrogate regret bounds for a tighter class of quadratic surrogates based on projection oracles.
\citet[Theorem 4.4]{nowak2019general} give even more general bounds, using a broader class of surrogates based on estimating a vector-valued expectation.
All of these works apply to a broad range of discrete target problems.
The main difference to our work is that their upper bounds are all for strongly convex surrogates,%
\footnote{These works express surrogate regret bounds with $\zeta^{-1}$ appearing on the left-hand side of eq.~\eqref{eq:surrogate-regret-bound-informal}, and thus the terms ``upper bound'' and ``lower bound'' are reversed from their terminology.}
whereas ours are for polyhedral surrogates.
\citet[Theorem 8]{osokin2017structured} and \citet[Theorem 4.5]{nowak2019general} also provide lower bounds, in the same spirit as our Theorem~\ref{thm:main-lower} but only for the classes of surrogates they study.
In particular, our results recover their bounds up to a constant factor.

@@

\paragraph{Target problems.}
We consider supervised machine learning problems where data points have features in $\X$ and labels in $\Y$, a finite set.
The \emph{target problem} is to learn a hypothesis mapping $\X$ to a \emph{report} (or \emph{prediction}) \emph{space} $\R$, possibly different from $\Y$.
For example, binary classification has $\Y = \R = \{-1,+1\}$, whereas for ranking problems $\R$ may be the set of permutations of $\Y$.
%, or $\R=\Y\cup\{\bot\}$ for classification with an abstain option.
In this paper, we assume $\R$ is a finite set.
%For example, standard binary classification has $\Y = \R = \{-1,+1\}$, whereas in a ranking problem, $\R$ is the set of all permutations of $\Y$.
The target problem is specified by the \emph{target loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r \in \R$ to the vector $\ell(r)$ of nonnegative loss values for each label, i.e. $\ell(r) = (\ell(r)_y)_{y\in\Y}$.
Given a hypothesis $g: \X \to \R$ and a data point $(x,y) \in \X \times \Y$, the loss is $\ell(g(x))_y$.
We make a minimal non-redundancy assumption on $\ell$, formalized in Section~\ref{subsec:elic}.
We may refer to $\ell$ as a \emph{discrete} target loss to emphasize our assumption that $\R$ and $\Y$ are finite.

\paragraph{Surrogate problems.}
We recall the surrogate risk minimization framework.
First, one constructs a \emph{surrogate loss function} $L:\reals^d\to\reals^\Y_+$.
Then, one minimizes it to learn a hypothesis of the form $h: \X \to \reals^d$.
Finally, one applies a \emph{link function} $\psi: \reals^d \to \R$, which maps $h$ to the implied target hypothesis $\psi \circ h$.%
\footnote{The term ``link function'' can carry a more specific meaning in the statistics literature, for example when discussing generalized linear models.
  Our usage here is more general: any map from surrogate reports to target reports is a valid link function, though perhaps not a calibrated one. \raf{Bo: check me}}
In other words, if a surrogate prediction $h(x) \in \reals^d$ implies a prediction $\psi(h(x)) \in \R$ for the target problem.
For example, in binary classification, the target problem is given by $0$-$1$ loss, $\ell(r)_y = \ones\{r\neq y\}$, with surrogate losses typically defined over $\reals$.
Common surrogate losses include hinge loss and logistic loss.
These surrogates are typically associated with the link $\psi(u) = \mathrm{sign}(u)$, which maps negative predictions to $-1$ and nonnegative predictions to $+1$.

@@

\section{Upper Bound: Polyhedral Surrogates} \label{sec:upper}
In this section, we describe the proof of Theorem~\ref{thm:main-upper}, that polyhedral surrogates guarantee linear regret transfers.
At a high level, the proof (whose details appear in Appendix~\ref{app:upper}) has two parts:
\begin{enumerate}
\item Fix $p\in\simplex$.
  Prove a regret bound for this fixed $p$, namely a constant $\alpha_p$ such that $R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p)$ for all $u\in\reals^d$.
      \item Apply this regret bound to each $p$ in a carefully chosen finite subset of $\simplex$.
        Argue that the maximum $\alpha_p$ from this finite set suffices for the overal regret bound.
\end{enumerate}
The first part will actually hold for any calibrated surrogate.
The second part relies on a crucial fact about polyhedral losses $L$: their properties $\Gamma=\prop{L}$ cover the whole simplex with only a finite number of polyhedral level sets~\cite{finocchiaro2019embedding}.
Thus, although the prediction space $\reals^d$ is infinite, one can restrict to just a finite set of prediction points and always have a global minimizer of expected surrogate loss.

\subsection{Linear transfer for fixed $p$}
First, we establish a linear transfer for any fixed conditional distribution $p$.
This holds for any calibrated surrogate, not necessarily polyhedral.
\begin{lemma} \label{lemma:fixed-p}
  Let $\ell: \R \to \reals_+^{\Y}$ be a discrete target loss and suppose the surrogate $L: \reals^d \to \reals_+^{\Y}$ and link $\psi: \reals^d \to \R$ are calibrated for $\ell$.
  Then for any $p \in \simplex$, there exists $\alpha_p \geq 0$ such that, for all $u \in \reals^d$,
    \[ R_{\ell}(\psi(u),p) \leq \alpha_p R_L(u,p) . \]
\end{lemma}
While this result is nice, it is also somewhat nonconstructive and potentially loose.
In Section~\ref{sec:constant}, we investigate the constant $\alpha_p$ for polyhedral losses in particular.

\subsection{Linear overall transfer function}
Given Lemma~\ref{lemma:fixed-p}, we might hope to obtain that, for any calibrated surrogate, there exists $\alpha = \sup_p \alpha_p$ such that $R_{\ell}(\psi(u),p') \leq \alpha R_L(u,p')$ for all $p'$.
However, we know this is false in general: not all surrogates yield linear regret transfers!
Indeed, for many surrogates, the supremum will be $+\infty$.

@@

The next lemma states that surrogate regret is linear in $p$ on any fixed level set $\Gamma_{u^*}$ of $\Gamma = \prop{L}$.
By combining this fact with Lemma~\ref{lemma:refines}, we obtain that target regret is linear on these level sets as well.
\begin{lemma} \label{lemma:linear-on-levelset}
  Suppose $(L,\psi)$ indirectly elicits $\gamma = \prop{\ell}$ and let $\Gamma = \prop{L}$.
  Then for any fixed $u,u^* \in \reals^d$ and $r \in \R$, the functions $R_L(u,\cdot)$ and $R_{\ell}(r,\cdot)$ are linear on $\Gamma_{u^*}$ in their second arguments.
\end{lemma}

A key fact we use about polyhedral losses is that they have a finite set of optimal sets.
% It requires that $L$ be \emph{minimizable:} for all $p \in \simplex$, there exists some optimal prediction $u$, i.e. where $\inprod{p}{L(u)} = \inf_{u' \in \reals^d} \inprod{p}{L(u')}$.
% Note that if $(L,\psi)$ indirectly elicits $\ell$ for some $\psi$ and $\ell$ then $L$ is minimizable.
% \raf{Fix discussion and proof: minimizability comes for free, since we assume $L(\cdot)_y \geq 0$ for all $y$.}
\begin{lemma} \label{lemma:polyhedral-finite}
  If $L: \reals^d \to \reals_+^{\Y}$ is polyhedral, then $\Gamma = \prop{L}$ has a finite set of level sets that union to $\simplex$.
  Moreover, these level sets are polytopes.
\end{lemma}
